---
title: "DDP_Course_Project"
author: "Emma Wei Chen"
date: "2025-07-17"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## App Description

### App Purpose
This application allows you to explore height prediction models using age.

### How to Use
1. Choose an age using the slider bar
2. Submit

You could explore the difference between boys and girls using the tabs.  

### Data Source
Simulated data is obtained from the *child_growth* dataset in the *doBy* package.
```{r}
library(ggplot2)
```

```{r echo = TRUE}
library(doBy)
data("child_growth")
my_data <- child_growth
my_data$gender <- factor(my_data$gender)
male_data <- subset(my_data, gender == "boy")
```

## Models

Two models are used to predict child height using age.  
1. Linear model  
2. Logistic model

## Model 1: Linear model
Using male data as an example here. 
Model fitting indicated by the red line. 

```{r echo = TRUE, warning=FALSE}
model1_male <- lm(height ~ age, data = male_data)

```

```{r echo = FALSE, warning=FALSE}
# Create a small data frame to plot the linear model line with color mapping for legend
linear_line_df <- data.frame(
  age = c(min(male_data$age), max(male_data$age))
)
linear_line_df$height <- coef(model1_male)[1] + coef(model1_male)[2] * linear_line_df$age
linear_line_df$model <- "Model 1: Linear"

p <- ggplot(male_data, aes(x = age, y = height)) +
          geom_point(position = "jitter", alpha = 0.5, color = "lightblue") +
          labs(
            x = "Age", 
            y = "Height"
          ) +
          xlim(c(1, 18)) +
          ylim(c(20, 210)) +
          theme_classic() +
          theme(
            text = element_text(size = 20)
          )
p <- p + geom_line(data = linear_line_df, aes(x = age, y = height), color = "red", size = 1)
p
```

## Model 2: Logistic model
Using male data as an example here. 
Model fitting indicated by the blue line. 

```{r echo = TRUE, warning=FALSE}
model2_male <- nls(height ~ Asym / (1 + exp((xmid - age)/scal)),
                      data = male_data,
                      start = list(Asym = 180, xmid = 13, scal = 2))

```

```{r echo = FALSE, warning=FALSE}
age_seq <- seq(1, 18, length.out = 200)
pred_male <- data.frame(
  age = age_seq,
  height = predict(model2_male, newdata = data.frame(age = age_seq)),
  gender = "boy"
)

# Add nonlinear model line with color mapped to model for legend
pred_male$model <- "Model 2: Logistic"  # make sure this column exists in pred_male
p <- p + geom_line(data = pred_male, aes(x = age, y = height), color = "blue", size = 1)

p
    
```